---
title: "reduction"
author: "Brock Friedrich"
date: "September 30, 2018"
output: html_document
---



1. Identify the key objectives. 
2. Screen the available variables, deciding on a list that is sensitive to the objectives and excludes obvious redundancies. 3. Perform exploratory analysis, examining graphical displays and correlation coefficients. 
4. Perform transformations as necessary. 
5. Examine a residual plot after fitting a rich model, performing further transformations and considering outliers. 
6. Use a computer-assisted technique for finding a suitable subset of explanatory variables, exerting enough control over the process to be sensitive to the questions of interest. 
7. Proceed with the analysis, using the selected explanatory variables.

Ramsey, Fred; Schafer, Daniel. The Statistical Sleuth: A Course in Methods of Data Analysis (Page 355). Cengage Textbook. Kindle Edition. 



1. Predict price of specific property
    - Select model based on minimization of RMSLE

2. List of variables that are sensitive to the objectives, excluding obvious redundancies
  - 




```{r fig.width = 30, fig.height = 30, eval = FALSE}



train %>% select(price.doc, full.sq, life.sq, floor, max.floor, material, build.year, num.room, kitch.sq, state, product.type, sub.area, area.m, raion.popul, green.zone.part, indust.part, children.preschool, preschool.quota, preschool.education.centers.raion, children.school, school.quota, school.education.centers.raion) %>%
  mutate(price.log = log(price.doc)) %>%
  gather(-price.log, key = "var", value = "value") %>% 
  ggplot(aes(x = value, y = price.log)) +
    geom_point() +
    facet_wrap(~ var, scales = "free") +
    theme_bw()

ggsave("test.png", width = 30, height = 30, units = "in")

```



```{r fig.width = 20, fig.height = 20}

c = colors(distinct = TRUE)
c.s <- c[sample(2:length(c), 1)]


scatterplotMatrix(train %>% 
                    select_if(is.numeric) %>% 
                    select(contains('cafe'))
                    , smooth=FALSE
                    , diagonal="histogram"
                    , col = c.s)
```


```{r}

# Cafe_Count Correlation Matrix

cafe_count <- train %>% 
  select_if(is.numeric) %>% 
  dplyr::select(contains('cafe.count')) %>%
  na.omit() # %>%
  # dplyr::select(1:5)


png(filename = './../figs/cafe_cor.png'
      , width = 40
      , height = 40
      , units = 'in'
      , res = 300)

library(GGally)
ggpairs(cafe_count)

dev.off()

```

All 'cafe_count' features are highly correlated. We will merge them into a single feature.

```{r}

cafe_count %>% head()

cafe_count <- cafe_count %>%
                 replace(is.na(.), 0) %>%
                 mutate(rowsum = rowSums(.))


plot(cafe_count$rowsum, train$price.doc)

# cafe_count replacement variable density
plot(density(cafe_count$rowsum)) # plots the results

```

The rowsum plot above is similar enough in shape to its component features that we may use it as a substitute during model selection.